Optical nanostructures design, fabrication, and applications for solar/thermal energy conversion

### 2017-02-11 submission.tex
Fixed syle

\documentclass[10pt,letterpaper]{article}
\usepackage{opex3}
\usepackage{color}
\usepackage{amsmath}
%%%%%%%%%%%%%%%%%%%%%
% REMOVE BEFORE SUBMISSION
\usepackage{amsmath,amssymb,graphicx}
\usepackage{dcolumn}%
%%\usepackage{array,multirow}
\usepackage{bm}%
\usepackage{cite}
\usepackage{pstool}%
\usepackage{array}
\usepackage{xcolor}
\usepackage{subcaption,subfloat} % lets you have multiple pictures next to each other
\usepackage{upgreek}
%\usepackage[numbers,sort&compress]{natbib}
\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{A\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{A\arabic{figure}}%
     }

@@

Operating at such high temperatures means that there will be a large amount of thermal emission from the absorbing surface, resulting in a loss of energy.  To reduce this loss, the thermal emittance of the absorbing surface must be minimized.  Here, we will define $\upepsilon_{abs}$ as the thermal emittance of an absorbing surface held at a specific temperature relative to the thermal emittance of a blackbody held at the same temperature.  This means that an absorbing surface with an $\upepsilon_{abs}$ of 0.5 at 1000$^\circ$C would have half the thermal emission of a blackbody at 1000$^\circ$C.  Note that the $\upepsilon_{abs}$ of a surface can change drastically with temperature if its reflectivity and absorbance change for different wavelengths of light.  This is because the spectral composition of blackbody radiation changes with temperature.  At the same time, the solar absorptance ($\upalpha_{sol}$) of the surface must be maximized to ensure a high power input into the device.

For a surface to have high $\upalpha_{sol}$ and low $\upepsilon_{abs}$, it must have a low reflectance and high absorbance in visible wavelengths (where most solar light is located), and a high reflectance in the near infra-red (NIR) region (where most thermal emission is located).  This is a type of spectrally selective surface.  These surfaces must also remain stable under the high operating temperatures found in ST systems.  The relative importance of high $\upalpha_{sol}$ and low $\upepsilon_{abs}$ can change due to changes in system parameters.  For example, higher operating temperatures increase thermal emission and place more importance on achieving a low $\upepsilon_{abs}$, while higher solar concentrations result in achieving a high $\upalpha_{sol}$ being more important.

Spectrally-selective surfaces are much studied in ST research 
because they can lead to high-efficiency systems.  While coatings for lower (\textless500$^\circ$C) temperatures have been extensively studied, they are generally not suitable for high temperature operation due to a lack of thermal stability \cite{A1}.  Some research has attempted to use silicon or germanium based absorbers, but their high solar reflectance necessitates the use of broad-band anti-reflective coatings which results in high $\upepsilon_{abs}$, and their performance degrades at high temperatures due to oxidation \cite{A2}.

Stacks of layered dielectric and metallic films can be used to control the reflectance of structures via multiple reflections and interference effects \cite{A3}.  Many different materials have been investigated for this purpose, including stacks using tungsten, molybdenum, titanium oxide, and magnesium fluoride that had an $\upepsilon_{abs}$\textless7\% and $\upalpha_{sol}$\textgreater94\% \cite{paper1_ref7,stacks2, A2}.  Unfortunately, fabrication of these surfaces requires vacuum deposition of multiple layers with precise thickness, which can be difficult.

Ceramic-metal composites (cermets) consist of metallic particles in a dielectric host that are often used as spectrally selective surfaces in ST applications.  The metallic particles in the cermet layer result in high $\upalpha_{sol}$ due to multiple reflections, and they are typically used on metallic substrates with high IR reflectance, resulting in low $\upepsilon_{abs}$ \cite{A2,A4,A5,A6,A7,A8,A9,A10}.  The disadvantages of cermets include sensitivity to oxygen at high temperatures and the requirement for vacuum fabrication methods.

@@

Periodic sub-wavelength gratings on tungsten substrates have been fabricated with an $\upalpha_{sol}$ of 82\% and $\upepsilon_{abs}$ of 5.6\% at 770$^\circ$C and were experimentally verified to be 
stable up to temperatures of 900 $^\circ$C \cite{A13}.  These structures cause standing wave resonances that can be tuned for solar absorption.

Sub-wavelength roughness on metallic substrates can also increase solar absorbance due to the surface acting as a graded index medium \cite{A13,A19}.  The $\upepsilon_{abs}$ of these surfaces can be kept low because NIR wavelengths are much longer than the dimensions of the roughness, so the surface appears smooth \cite{A14}.  An advantage of these types of structures is that they do not require periodicity, and randomness can in fact be an advantage \cite{me1}.  Simulations have shown pseudo-random nanocones on a tungsten substrate to have an $\upalpha_{sol}$ of 97\% and $\upepsilon_{abs}$ of 16\% at 1400 $^\circ$C \cite{me1}.  Experimental data on surface roughness created by laser-sintering of nanoparticles have shown an $\upalpha_{sol}$ of 83\% and $\upepsilon_{abs}$ of 11.6\% \cite{g21}.

@@

\begin{table}
	\caption{Efficiency, relative solar absorption, and relative thermal emission at a temperature of 1700 K of selected absorbing surfaces.}
	\label{abs_eff_table}
	\begin{center}
		\begin{tabular}{|llll|}
			%\begin{tabular}{|p{5.3cm}|p{2.6cm}|}
			\hline
			Absorber type & Absorber efficiency & $\upalpha_{sol}$ & $\upepsilon_{abs}$\\
			\hline	
			Ideal solar absorber & 0.83 & 0.87 & 0.04\\
			Pseudo random nano-cones in W & 0.80 & 0.97 & 0.16~\cite{me1}\\
			W pyramidal nanostructures & 0.79 & 0.92 & 0.13~\cite{paper1_ref4}\\
			Mo-SiO$_2$ cermet & 0.77 & 0.93 & 0.16~\cite{cermet6}\\
			Carbon nanotubes & 0.74 & 0.99 & 0.95~\cite{MIT_paper}\\
			1-D photonic crystal on W & 0.74 & 0.80 & 0.06~\cite{SKY_JPE_2015}\\
			Blackbody absorber & 0.73 & 1.00 & 1.00\\
			Anti-reflection coating on W & 0.67 & 0.73 & 0.05~\cite{SKY_JPE_2015}\\
			W cavities & 0.59 & 0.74 & 0.15~\cite{exp_russia}\\
			Surface-relief grating on W & 0.49 & 0.53 & 0.05~\cite{paper1_ref6}\\
			Bare W & 0.41 & 0.44 & 0.04~\cite{palik}\\
			\hline
		\end{tabular}
	\end{center}
\end{table}

The absorbing surfaces for STPV devices are similar to those used in ST systems, although higher operating temperatures (up to around 1750 K) 
make thermal stability a more prominent concern, and high levels of solar concentration (\textgreater4000) make a high $\upalpha_{sol}$ of 
paramount concern.  This means that nanotextured absorbing surfaces are a very good match for these systems.  Most experimental STPV systems 
to date have utilized blackbody absorbing surfaces \cite{exp_tokyo,exp_madrid,exp_russia,MIT_paper}, leaving room for much improvement by using 
selective absorbing surfaces. Recent results have reported record efficiencies~\cite{g11,SKY_JPE_2015} using both 
selective absorbers and selective emitters. A yttria-stabilized zirconia and tungsten stack was used as a selective absorber in an experimental system~\cite{SKY_JPE_2015}, 
but while it's thermal emission was low, its performance was hindered by a low $\upalpha_{sol}$ of 80\%.  Simulations of various surfaces 
have shown large gains in system efficiency from the use of nanotextured selective, such as pseudo-random 
nanocones with an $\upalpha_{sol}$ of 97\% and $\upepsilon_{abs}$ of 16\% \cite{me1}, or pyramidal nanostructures in tungsten 
with an $\upalpha_{sol}$ of 92\% and $\upepsilon_{abs}$ of 13\% \cite{paper1_ref4} but none have been experimentally 
demonstrated in a working STPV system to date \cite{paper1_ref5,paper1_ref6}.

@@

Table \ref{abs_eff_table} shows the $\upalpha_{sol}$ and $\upepsilon_{abs}$ of some absorbing surfaces, as well as a calculated surface efficiency.  The quantity $\eta_{abs}$ is given by
\begin{align}
\label{overall_sss_eq}\eta_{abs}(T)& = \frac{\int_{0}^{\infty}\left\{E_{inc}(\lambda)\alpha(\lambda)-\epsilon(\lambda)B(\lambda,T)\right\}d\lambda}{\int_{0}^{\infty}E_{inc}(\lambda)d\lambda}\\
\label{e_incident}E_{inc}(\lambda) &= C \: \eta_{conc} \: E_{sun}(\lambda),
\end{align}
where $\alpha(\lambda)$ is the spectral absorption of the surface, $\epsilon(\lambda)$ is the spectral emittance of the surface, $C$ is the concentration ratio of incoming sunlight, 
$\eta_{conc}$ is the solar concentration efficiency, $E_{sun}(\lambda)$ is the 
spectral irradiance of the sun at the earth's surface, $B(\lambda, T)$ is 
Planck's law for blackbody radiation, and $E_{inc}(\lambda)$ is the spectral 
energy incident on the absorbing surface.

>>>>

\documentclass[10pt,letterpaper]{article}
\usepackage{opex3}
\usepackage{color}
\usepackage{amsmath}
%%%%%%%%%%%%%%%%%%%%%
% REMOVE BEFORE SUBMISSION
\usepackage{amsmath,amssymb,graphicx}
\usepackage{dcolumn}%
\usepackage{array,multirow}
\usepackage{bm}%
\usepackage{cite}
\usepackage{pstool}%
\usepackage{array}
\usepackage{xcolor}
\usepackage{subcaption,subfloat} % lets you have multiple pictures next to each other
%%\usepackage{upgreek}
%\usepackage[numbers,sort&compress]{natbib}
\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{A\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{A\arabic{figure}}%
     }

@@

Operating at such high temperatures means that there will be a large amount of thermal emission from the absorbing surface, resulting in a loss of energy.  To reduce this loss, the thermal emittance of the absorbing surface must be minimized.  Here, we will define $\epsilon_{abs}$ as the thermal emittance of an absorbing surface held at a specific temperature relative to the thermal emittance of a blackbody held at the same temperature.  This means that an absorbing surface with an $\epsilon_{abs}$ of 0.5 at 1000$^\circ$C would have half the thermal emission of a blackbody at 1000$^\circ$C.  Note that the $\epsilon_{abs}$ of a surface can change drastically with temperature if its reflectivity and absorbance change for different wavelengths of light.  This is because the spectral composition of blackbody radiation changes with temperature.  At the same time, the solar absorptance ($\alpha_{sol}$) of the surface must be maximized to ensure a high power input into the device.

For a surface to have high $\alpha_{sol}$ and low $\epsilon_{abs}$, it must have a low reflectance and high absorbance in visible wavelengths (where most solar light is located), and a high reflectance in the near infra-red (NIR) region (where most thermal emission is located).  This is a type of spectrally selective surface.  These surfaces must also remain stable under the high operating temperatures found in ST systems.  The relative importance of high $\alpha_{sol}$ and low $\epsilon_{abs}$ can change due to changes in system parameters.  For example, higher operating temperatures increase thermal emission and place more importance on achieving a low $\epsilon_{abs}$, while higher solar concentrations result in achieving a high $\alpha_{sol}$ being more important.

Spectrally-selective surfaces are much studied in ST research 
because they can lead to high-efficiency systems.  While coatings for lower (\textless500$^\circ$C) temperatures have been extensively studied, they are generally not suitable for high temperature operation due to a lack of thermal stability \cite{A1}.  Some research has attempted to use silicon or germanium based absorbers, but their high solar reflectance necessitates the use of broad-band anti-reflective coatings which results in high $\epsilon_{abs}$, and their performance degrades at high temperatures due to oxidation \cite{A2}.

Stacks of layered dielectric and metallic films can be used to control the reflectance of structures via multiple reflections and interference effects \cite{A3}.  Many different materials have been investigated for this purpose, including stacks using tungsten, molybdenum, titanium oxide, and magnesium fluoride that had an $\epsilon_{abs}$\textless7\% and $\alpha_{sol}$\textgreater94\% \cite{paper1_ref7,stacks2, A2}.  Unfortunately, fabrication of these surfaces requires vacuum deposition of multiple layers with precise thickness, which can be difficult.

Ceramic-metal composites (cermets) consist of metallic particles in a dielectric host that are often used as spectrally selective surfaces in ST applications.  The metallic particles in the cermet layer result in high $\alpha_{sol}$ due to multiple reflections, and they are typically used on metallic substrates with high IR reflectance, resulting in low $\epsilon_{abs}$ \cite{A2,A4,A5,A6,A7,A8,A9,A10}.  The disadvantages of cermets include sensitivity to oxygen at high temperatures and the requirement for vacuum fabrication methods.

@@

Periodic sub-wavelength gratings on tungsten substrates have been fabricated with an $\alpha_{sol}$ of 82\% and $\epsilon_{abs}$ of 5.6\% at 770$^\circ$C and were experimentally verified to be 
stable up to temperatures of 900 $^\circ$C \cite{A13}.  These structures cause standing wave resonances that can be tuned for solar absorption.

Sub-wavelength roughness on metallic substrates can also increase solar absorbance due to the surface acting as a graded index medium \cite{A13,A19}.  The $\epsilon_{abs}$ of these surfaces can be kept low because NIR wavelengths are much longer than the dimensions of the roughness, so the surface appears smooth \cite{A14}.  An advantage of these types of structures is that they do not require periodicity, and randomness can in fact be an advantage \cite{me1}.  Simulations have shown pseudo-random nanocones on a tungsten substrate to have an $\alpha_{sol}$ of 97\% and $\epsilon_{abs}$ of 16\% at 1400 $^\circ$C \cite{me1}.  Experimental data on surface roughness created by laser-sintering of nanoparticles have shown an $\alpha_{sol}$ of 83\% and $\epsilon_{abs}$ of 11.6\% \cite{g21}.

@@

\begin{table}
	\caption{Efficiency, relative solar absorption, and relative thermal emission at a temperature of 1700 K of selected absorbing surfaces.}
	\label{abs_eff_table}
	\begin{center}
		\begin{tabular}{|llll|}
			%\begin{tabular}{|p{5.3cm}|p{2.6cm}|}
			\hline
			Absorber type & Absorber efficiency & $\alpha_{sol}$ & $\epsilon_{abs}$\\
			\hline	
			Ideal solar absorber & 0.83 & 0.87 & 0.04\\
			Pseudo random nano-cones in W & 0.80 & 0.97 & 0.16~\cite{me1}\\
			W pyramidal nanostructures & 0.79 & 0.92 & 0.13~\cite{paper1_ref4}\\
			Mo-SiO$_2$ cermet & 0.77 & 0.93 & 0.16~\cite{cermet6}\\
			Carbon nanotubes & 0.74 & 0.99 & 0.95~\cite{MIT_paper}\\
			1-D photonic crystal on W & 0.74 & 0.80 & 0.06~\cite{SKY_JPE_2015}\\
			Blackbody absorber & 0.73 & 1.00 & 1.00\\
			Anti-reflection coating on W & 0.67 & 0.73 & 0.05~\cite{SKY_JPE_2015}\\
			W cavities & 0.59 & 0.74 & 0.15~\cite{exp_russia}\\
			Surface-relief grating on W & 0.49 & 0.53 & 0.05~\cite{paper1_ref6}\\
			Bare W & 0.41 & 0.44 & 0.04~\cite{palik}\\
			\hline
		\end{tabular}
	\end{center}
\end{table}

The absorbing surfaces for STPV devices are similar to those used in ST systems, although higher operating temperatures (up to around 1750 K) 
make thermal stability a more prominent concern, and high levels of solar concentration (\textgreater4000) make a high $\alpha_{sol}$ of 
paramount concern.  This means that nanotextured absorbing surfaces are a very good match for these systems.  Most experimental STPV systems 
to date have utilized blackbody absorbing surfaces \cite{exp_tokyo,exp_madrid,exp_russia,MIT_paper}, leaving room for much improvement by using 
selective absorbing surfaces. Recent results have reported record efficiencies~\cite{g11,SKY_JPE_2015} using both 
selective absorbers and selective emitters. A yttria-stabilized zirconia and tungsten stack was used as a selective absorber in an experimental system~\cite{SKY_JPE_2015}, 
but while it's thermal emission was low, its performance was hindered by a low $\alpha_{sol}$ of 80\%.  Simulations of various surfaces 
have shown large gains in system efficiency from the use of nanotextured selective, such as pseudo-random 
nanocones with an $\alpha_{sol}$ of 97\% and $\epsilon_{abs}$ of 16\% \cite{me1}, or pyramidal nanostructures in tungsten 
with an $\alpha_{sol}$ of 92\% and $\epsilon_{abs}$ of 13\% \cite{paper1_ref4} but none have been experimentally 
demonstrated in a working STPV system to date \cite{paper1_ref5,paper1_ref6}.

@@

Table \ref{abs_eff_table} shows the $\alpha_{sol}$ and $\epsilon_{abs}$ of some absorbing surfaces, as well as a calculated surface efficiency.  The quantity $\eta_{abs}$ is given by
\begin{align}
\label{overall_sss_eq}\eta_{abs}(T)& = \frac{\int_{0}^{\infty}\left\{E_{inc}(\lambda)\alpha(\lambda)-\epsilon(\lambda)B(\lambda,T)\right\}d\lambda}{\int_{0}^{\infty}E_{inc}(\lambda)d\lambda}\\
\label{e_incident}E_{inc}(\lambda) &= C \: \eta_{conc} \: E_{sun}(\lambda),
\end{align}
where $\alpha(\lambda)$ is the spectral absorption of the surface, $\epsilon(\lambda)$ is the spectral emittance of the surface, $C$ is the concentration ratio of incoming sunlight, 
$\eta_{conc}$ is the solar concentration efficiency, $E_{sun}(\lambda)$ is the 
spectral irradiance of the sun at the earth's surface, $B(\lambda, T)$ is 
Planck's law for blackbody radiation, and $E_{inc}(\lambda)$ is the spectral 
energy incident on the absorbing surface.
